---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fivestars

<!-- badges: start -->
<!-- [![CRAN status](https://img.shields.io/cran/v/fivestars?style=flat-square&logo=R&label=CRAN)](https://CRAN.R-project.org/package=fivestars)  -->
[![Dev status](https://img.shields.io/github/r-package/v/tanho63/fivestars/main?label=dev%20version&style=flat-square&logo=github)](https://fivestars.dynastyprocess.com/)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg?style=flat-square)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- [![R build status](https://img.shields.io/github/workflow/status/tanho63/fivestars/R-CMD-check?label=R%20check&style=flat-square&logo=github)](https://github.com/tanho63/fivestars/actions) -->
<!-- [![Codecov test coverage](https://img.shields.io/codecov/c/github/tanho63/fivestars?label=codecov&style=flat-square&logo=codecov)](https://codecov.io/gh/tanho63/fivestars?branch=main) -->

<!-- badges: end -->

The goal of {fivestars} is to generate star ratings with HTML and CSS.

## Installation

Install the development version from GitHub with:

```{r eval = FALSE}
install.packages("fivestars", repos = "https://tanho63.r-universe.dev")

# or use remotes/devtools
# install.packages("remotes")
remotes::install_github("tanho63/fivestars")
```

## Usage

```{r}
library(fivestars)
```

`use_fivestars()` adds the appropriate CSS and allows for some configuration of defaults (star size, colour, and background).

```{r}
use_fivestars(
  star_size = "20px", # default is "larger"
  star_color = "#fc0", # default
  star_background = "#999" # default
)
```

Minimal usage of the `fivestar` function looks like this:

```{r}
fivestar(rating = 3.5)
```

<br>
The output can be further customized with some arguments, e.g.
```{r}
fivestar(rating = 1.2,
         label = "Poor",
         label_pos = "right",
         aria_label = "This item is rated 'Poor'",
         star_color = "#d13", 
         star_background = "#000")
```

